### 2022-06-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@c70bb0c32fc9f7ee1cd0c8eef075914e1493ff52 🚀

In this section, we will assume a network of connectance \(\rho\),
\emph{i.e.} having \(\rho S^2\) interactions (where \(S\) is the species
richness), and \((1-\rho) S^2\) non-interactions. Therefore, the vector
describing the \emph{true} state of the network (assumed to be an
unweighted, directed network) is a column vector
\(\mathbf{o}^T = [\rho, \qquad (1-\rho)]\) (we can safely drop the
\(S^2\) terms, as we will work on the confusion matrix, which ends up
expressing \emph{relative} values). We will apply skill and bias to this
matrix, and measure how a selection of performance metrics respond to
changes in these values, in order to assess their suitability for model
evaluation.

@@

In order to write the values of the confusion matrix for a hypothetical
classifier, we need to define two characteristics: its skill, and its
bias. Skill, here, refers to the propensity of the classifier to get the
correct answer (\emph{i.e.} to assign interactions where they are, and
to not assign them where they are not). A no-skill classifier guesses at
random, \emph{i.e.} it will guess interactions with a probability
\(\rho\). The predictions of a no-skill classifier can be expressed as a
row vector \(\mathbf{p} = [\rho (1-\rho)]\). The confusion matrix
\(\mathbf{M}\) for a no-skill classifier is given by the element-wise
(Hadamard, outer) product of these vectors
\(\mathbf{o} \odot \mathbf{p}\), \emph{i.e.}

@@

In order to regulate the skill of this classifier, we can define a skill
matrix \(\mathbf{S}\) with diagonal elements equal to \(s\), and
off-diagonal elements equal to \((1-s)\), and re-express the
skill-adjusted confusion matrix as \(\mathbf{M} \odot \mathbf{S}\),
\emph{i.e.}

>>>>

In this section, we will assume a network of connectance \(\rho\),
\emph{i.e.} having \(\rho S^2\) interactions (where \(S\) is the species
richness), and \((1-\rho) S^2\) non-interactions. Therefore, the vector
describing the \emph{true} state of the network (assumed to be an
unweighted, directed network) is a column vector
\(\mathbf{o}^T = [\rho, (1-\rho)]\) (we can safely drop the \(S^2\)
terms, as we will work on the confusion matrix, which ends up expressing
\emph{relative} values). We will apply skill and bias to this matrix,
and measure how a selection of performance metrics respond to changes in
these values, in order to assess their suitability for model evaluation.

@@

In order to write the values of the confusion matrix for a hypothetical
classifier, we need to define two characteristics: its skill, and its
bias. Skill, here, refers to the propensity of the classifier to get the
correct answer (\emph{i.e.} to assign interactions where they are, and
to not assign them where they are not). A no-skill classifier guesses at
random, \emph{i.e.} it will guess interactions with a probability
\(\rho\). The predictions of a no-skill classifier can be expressed as a
row vector \(\mathbf{p}^T = [\rho, (1-\rho)]\). The confusion matrix
\(\mathbf{M}\) for a no-skill classifier is given by the element-wise
(Hadamard, outer) product of these vectors
\(\mathbf{o} \odot \mathbf{p}\), \emph{i.e.}

@@

In order to regulate the skill of this classifier, we can define a skill
matrix \(\mathbf{S}\) with diagonal elements equal to \(s\), and
off-diagonal elements equal to \((1-s)\), which allows to regulate how
many predictions are wrong, under the assumption that the bias is the
same (\emph{i.e.} the classifier is as likely to make a false positive
or a false negative). The skill-adjusted confusion matrix is
\(\mathbf{M} \odot \mathbf{S}\), \emph{i.e.}
